SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-08 paper/experiments.tex
table with cheap comparisison

@@

\begin{table}[!ht]
\centering
\def\arraystretch{1.6}
\caption{
{\bf Activity regulation of molecules and corresponding connectivity of the graph.}}
  \begin{tabular}{|c|c|c|c|}
    \hline
  {\multirow{2}{*}{\textbf{Version}}}  & {\multirow{2}{*}{\textbf{Constraints}}} &  \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
   \cline{3-4}
   {} & {} & \textbf{\textbf{Least}} & \textbf{Highest}\\
    %\hhline{~--}
    \hline

>>>>

\begin{tikzpicture}

  \begin{axis}[title  = CBMC Vs Z3 encoding for N $\equal$ 5 (in secs),
    xbar,
    y axis line style = { opacity = 0 },
    axis x line       = none,
    tickwidth         = 0pt,
    enlarge y limits  = 0.32,
    enlarge x limits  = 0.04,
    symbolic y coords = {Version F, Version E, Version C, Version A},
    nodes near coords,
    legend pos=outer north east,
  ]
  \legend{CBMC, Z3}
  \addplot coordinates { (3053.8,Version A)         (500.03,Version C)
                         (890.84,Version E)  (2482.71,Version F) };
  \addplot coordinates { (7.7,Version A)         (7.60,Version C)
                         (10.27,Version E)   (33.36,Version F)  };

  \end{axis}
\end{tikzpicture}

@@

\begin{table}[!ht]
\centering
\def\arraystretch{1.6}
\caption{
{\bf Activity regulation of molecules and corresponding connectivity of the graph.}}
  \begin{tabular}{|c|c|c|c|}
    \hline
  {\multirow{2}{*}{\textbf{Version}}}  & {\multirow{2}{*}{\textbf{Constraints}}} &  \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
   \cline{3-4}
   {} & {} & \textbf{\textbf{Least connected}} & \textbf{Sampling: Guarantee}\\
    %\hhline{~--}
    \hline
